---
title: "Appendix"
---

```{r, include = FALSE, message = FALSE, warning = FALSE, echo = FALSE}
source('data_setup.R')
```

## Appendix A: PE Knowledge Assessment Items

The following 39 items comprise the PE knowledge assessment, organized by SHAPE National Standard.

### Standard 2

S2 Analyzes physical development across the lifespan that influences physical activity choices

S2PT1.	Which of the following is the most accurate statement about physical activity levels?
A.  If children are not physically active, they won’t be physically active when       they are adults.
B.  Physical activity patterns stay the same as people age.
C.  Children and older adults are not that physically active.
D.  Physical activity patterns change as people age.

S2PT2.	Tommy’s grandmother played basketball while growing up and still rides a bike and walks regularly.  All of the following are benefits that Tommy’s grandmother could realize from physical activity, except:
A.  She sleeps better.
B.  She strengthened her bones to help resist osteoporosis. 
C.  She has sore muscles.  
D.  She has stronger heart and lungs.

S2PT3.	Mohammad is ahead of his peers in terms of motor skill development, which may be because of more:
A.  Maturity and practice.
B.  Instruction and speed.
C.  Practice, instruction and body size.
D.  Instruction, practice and maturity.

S2PT4.	As you continue to mature, which of the following is most likely to happen?
A.  I will get faster and stronger as I grow older, and that affects my skills.
	B.  My skills will stay the same if I continue to practice.
	C.  My skills in most activities will increase if I practice.
	D.  My skills will be better immediately.


### Standard 3

S3 Implements a personal physical activity plan that is part of a healthful lifestyle

S2PT5.   A pedometer is usually used to record how physically active you are by: 
	•	Recording your peddling action while you ride your bike.
	•	Measuring your average heart rate while you walk.
	•	Counting the number of steps you take during physical activity.
	•	Recording the number of physical activities in which you participate weekly.


S3PT6.   You should choose activities for your personal physical activity plan that: 
	•	You can fit into your schedule.  
	•	You can perform with enjoyment.
	•	Your friends enjoy doing. 
	•	Are provided by your local recreation program.

Employs self-management skills to maintain a physically active life

S3PT7.   Which of the following are benefits of being physically fit?
	•	Decreased heart rate and appetite. 
	•	Improved self-esteem and reduced stress. 
	•	Increased resting heart rate and lowered stress.
	•	More energy and less need for sleep.

S3PT8.   A physically active person accumulates up to 60 minutes a day of moderate-to-      vigorous physical activity. Which of the following best describes a “physically       active lifestyle?” 
	•	Walks to school, mows grass and rakes leaves, cleans house, completes a personal fitness workout 5 to 6 days a week, plays on the school tennis team.
	•	Rides the bus to school, participates in PE class 2 days a week, works at the local grocery store stocking shelves on weekends.
	•	Completes homework each day, completes chores at home, practices daily with the marching band at school, walks to school.
	•	Participates in a bowling league 1 to 2 days a week, volunteers at the community library restocking books 2 to 3 days a week, runs a mile 3 days a week.  

S3PT9.    Which of the following plans demonstrates the most physically active lifestyle?
	•	Work out at the local fitness center at least 3 days a week. 
	•	Swim or play soccer or tennis for 60 minutes at least 5 days a week.
	•	Run a mile at least 2 days a week.
	•	Perform a weight-lifting program at least 3 days a week.

S3PT10.    Which group of activities would most likely help to improve all components of         health-related physical fitness if added to your personal physical activity plan?
	•	Biking, volleyball, swimming.
	•	Soccer, basketball, softball.
	•	Gymnastics, running, bowling. 
	•	Yoga, weight lifting, running.

Achieves levels of health-related criterion referenced standards for fitness. 

S3PT11.    The percentages of fat, muscle, bone and water in the body are fitness components         called:  
	•	Weight management. 
	•	Nutritional balance. 
	•	Body composition.
	•	Physical structure.

S3PT12.   Running for distance or time can be used to measure:   
	•	Flexibility.
	•	Aerobic endurance.
	•	Distance capacity.
	•	Muscle strength.

Demonstrates the skill, knowledge and desire to monitor and adjust activity levels to meet personal fitness needs.

S3PT13.    You can increase the intensity of your workout by:  
	•	Increasing distance & speed.
	•	Decreasing speed & distance.
	•	Increasing time & decreasing distance. 
	•	Increasing time & decreasing repetitions.

S3PT14.    In the FITT guidelines, “frequency” refers to:
	•	How long you exercise.
	•	How much time you allow between repetitions. 
	•	How often you exercise.
	•	The number of weeks in a workout plan.

S3PT15.   When you reach your initial goal for improved physical fitness, you should apply the          principle of “progression” to safely adjust your work-out plan to continue fitness          improvement by:
	•	Increasing the intensity of your workout.
	•	Increasing the number of “no-workout” days per week.
	•	Keeping your workout the same.
	•	Work out at a lower level of intensity.

S3PT16.    The type of activities to improve aerobic endurance must be able to ________          throughout the activity.
	•	Keep the heart rate at the target heart rate level.
	•	Keep the heart rate at a resting level.
	•	Change the heart rate.
	•	Allow the heart rate to recover.

S3PT17.   My goal is to lose weight safely and decrease my percentage of body fat in the next   four weeks by ___________.
	•	Walking daily, reducing water consumption, eating more whole grain bread and eliminating fatty foods.
	•	Walking 30 minutes daily, eating more fruit and vegetables, and consuming more water and fewer calories.
	•	Jogging every other day, avoiding meat and bread, eating more fruit, and drinking 8 glasses of water each day. 
	•	Walking 3 times per week, cutting my calorie intake by 25 percent, eating more protein, and increasing my water intake daily.

S3PT18.    My goal is to complete the mile run without stopping to rest by doing the following          for four weeks:
	•	Alternately run and walk at least 5 days a week, increasing the distance I run gradually.
	•	Walk briskly for 1¼ miles at least 5 days a week. 
	•	Alternately run and walk at least every other day.
	•	Walk 1 mile briskly 3 days the first week and add ½ mile each week after that.

S3PT19.    When planning your exercise program, you should start by:
	•	Using a plan of physical fitness activities based on nationally set goals.
	•	Keeping a log of your participation in all physical activities.
	•	Reviewing your personal fitness test scores and setting personal fitness goals.
	•	Deciding how much time you have to exercise.

S3PT20.   When the length of a run is changed from 1 mile to 1¼ miles, what principle is          being applied?
	•	Intensity. 
	•	Specificity.
	•	Frequency.
	•	Progression.

S3PT21.    When adjusting your workout to increase flexibility, stretch each muscle group          beyond the distance required by your normal activities and until:
	•	You cannot stand the pain.
	•	The muscle becomes tight without painful discomfort.
	•	You reach the recommended distance for your age group.
	•	Your reach your long-term goal distance.

S3PT22.    A personal fitness workout plan for improving total health-related fitness should    include goals based on:  
	•	Personal evaluation, with specific activities to address body composition.
	•	Published charts of expectations for a person of your height and weight, with specific activities to address all fitness components. 
	•	Personal test results, specific activities to address each component, and realistic expectations. 
	•	Personal test results and desired achievement of specific sports skills.

Scenario: Goal-Setting. Use to answer questions 21 & 22.

Jamal wants to set up a fitness plan that will improve his fitness levels. He is 15 years old and is in high school.  He appears to be healthy but is overweight.  Below are his pre-test scores and goals for his fitness plan.  Read the goals and answer the questions below.

Jamal’s Goals for September through January 31.

Fitness Component
Pre-Test
Goal
Muscle endurance
Push-ups = 1
3

Curl-ups = 12
20+
Body composition
32% body fat
32% body fat or less
Aerobic endurance
22-minute mile
18-minute mile




S3PT23.   Jamal has set a goal for improving his push-up score. Which of the following work-        out plans is most likely to help him reach his goal?
	•	Complete 3 sets of up to 10 modified push-ups each, with hands on a table and feet on the floor, every other day for 3 weeks. 
	•	Complete 3 sets of up to 10 modified push-ups each, with hands on a table and feet on the floor, at least 2 days a week for 3 weeks.
	•	Complete 3 sets of up to 10 modified push-ups each, with hands on a table and feet on the floor, at least once a week for 3 weeks. 
	•	Complete as many push-ups as you can 3 days a week for 3 weeks.  

S3PT24.    Jamal has set a goal of improving his curl-up score by completing 3 sets of up to 10          curl-ups each, every other day for 3 weeks.  If he reaches his goal of 20 curl-ups          without rest, Jamal should adjust the goal and continue the workout for 3 more          weeks, but:
	•	Increase the number of repetitions to up to 15 in each set. 
	•	Keep the number of repetitions in each set the same. 
	•	Decrease the number of repetitions and increase the number of sets in each workout.
	•	Complete as many curl-ups as possible in each workout.

S3PT25.    When designing a conditioning program to improve health-related fitness, you          should first look at your current fitness test scores to determine realistic goals          around which to create a workout plan.  Which set of guidelines must you consider          for each of the activities/exercises in the daily plan?
	•	Frequency, intensity, time and specific type of exercise needed to address each health-related fitness component.
	•	Personal needs for sleeping, studying, working and eating.
	•	Your physical activity level and interests.
	•	Nutrition needs and eating habits.






Applies problem-solving techniques. 

S3PT26.   If Matt has the solution to a problem that his group is trying to answer, he should:
    	A.  Tell the group the answer quickly so that it can be implemented quickly.
    	B.  Become the group leader and guide group members to complete the task using       his solution.
C.  Present his idea to the group and ask for alternative ideas.
    	D.  Task group members with solving the problem consistent with his solution.

S3PT27. 	How should Samantha act when the official makes a call with which she disagrees?
    		A.  Let everyone know that it was a bad call.
    		B.  Accept the official’s call and play by the spirit of the game.
    		C.  Point out the mistake to the official.
    		D.  Wait until after the game and then tell the official that it was a bad call.


Demonstrates responsibility for following safe practices, rules, procedures and etiquette in physical activity settings.

S3PT28.   What should you do if an opponent drops his/her racket accidentally during a competitive net game and he/she cannot play the point?
    A.  Offer to replay the point. 
    B.  Continue to play.
    C.  Stop play and give yourself a point. 
    D.  Declare that dropping a racket is a safety violation, which makes you the winner. 

Exhibits supportive behavior. 

S3PT29.   Good sportsmanship means that, when you win a game, you should:       
    	A.  Not say or do anything.
    	B.  Thank the opposing team for a good game.
    	C.  Congratulate your teammates.
    	D.  Celebrate your win enthusiastically


### Standard 4

Recognizes the different benefits associated with participation in various types of physical activities

S4PT30.   Of the following activities that Kaitlin enjoys regularly, which should she select if she wants the most fitness benefit? 
    	A.  Lap swimming.
    	B.  Tai chi.
    	C.  Walking.
    	D.  Volleyball.

 S4PT31.   Charice wants to increase her participation in physical activity so that she is active every day.  What criteria should she use for selecting an activity?
    	A. Select the activity that her friends say they like to do.
    	B. Select an activity that she doesn't know how to do.
    	C. Select an activity that is enjoyable to her.
    	D. Select the most popular activity among classmates.
	
S4PT32.   Which would best serve to help Carla improve or maintain her flexibility?
    	A.  Weight training.    
    	B.  Curl-ups.
    	C.  Line dancing.
    	D.  Gymnastics.

S4PT33.   Devin’s doctor has warned him of the risk factors associated with his obesity and has recommended that he improve his cardiorespiratory fitness.  Devin should begin by:
    	A.  Taking a brisk evening walk every day.
    	B.  Jogging every day for 30 minutes. 
    	C.  Completing 3 to 4 sprints down the football field 3 times a week.
    	D.  Jogging three times a week for 30 minutes. 

S4PT34.  Which one of the following lifestyle changes to improve physical activity doesn’t require much effort and could improve your health?
    	A.  Taking the stairs instead of the elevator.    
    	B.  Playing basketball at a local community league.   
    	C.  Organizing a group to go on a backpacking trip.
    	D.  Working out to an exercise video every morning before going to school.

Recognizes the attraction of participation in various physical activities.

S4PT35.   Tara’s favorite physical activity is mountain biking. She might enjoy that activity most because:
A.  She enjoys a challenge and being outdoors.
    	B.  It requires inexpensive equipment.
C.  She can do it anywhere.
D.  She is not skilled at most other activities.

S4PT36.   Your friend is not very active.  How can you best encourage him to start exercising?
    	A.  Invite him to join you in an enjoyable activity. 
    	B.  Show him a list of those activities that you believe are fun and challenging.
    	C.  Encourage him to seek the advice of athletes.
    	D.  Give him a handout from class on the benefits of being active. 

S4PT37.   Students who are physically active and watch what they eat usually:
A.  Earn better grades in school.
   	B.  Are not well liked by other students.
   	C.  Are healthier.
   	D.  Don’t have a lot of free time.

S4PT38.  A good choice of physical activity for a person who wants to be physically active but hates sports that include running would be: 
   		A.  Jogging.
   		B.  Dance.
   		C.  Soccer.
   		D.  Wii sports.

S4PT39.   Other than health benefits, why would Carli value rock climbing, mountain biking and kayaking?
    	A.  Social interaction.
B.  The challenge.
C.  Self-expression.
    	D.  Cooperation.


## Appendix B: Grade and Race Distribution Tables

```{r, echo=FALSE}
ipe_data %>%
  mutate(Grade = ifelse(Grade == 0 | is.na(Grade), "Not Reported", as.character(Grade))) %>%
  group_by(Grade) %>%
  summarize(Count = n())%>%
  mutate(Percentage = round(Count/nrow(ipe_data),3)) %>%
  arrange(factor(Grade, levels = c("9", "10", "11", "12", "Not Reported"))) %>%
  kable(col.names = c("Grade", "n", "%"), 
        caption = "Grade Distribution",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("hold_position", "striped"))

ipe_data %>%
  group_by(race_2) %>%
  mutate(race_2 = str_to_title(race_2)) %>%
  summarize(Count = n()) %>%
  mutate(Percentage = round(Count/nrow(ipe_data),3)) %>%
  arrange(factor(race_2, levels = c("White", "Black", "Other", "Unknown"))) %>%
  kable(col.names = c("Race", "n", "%"), 
        caption = "Race Distribution",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("hold_position", "striped"))
```

